<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-30 MainAnalysis.Rmd
Capturing output of fit_all() runs and sending to a txt file

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))

@@

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))
write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""), row.names = FALSE)

>>>>

### do 1-Compartment fit
system.time(
  capture.output(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_1comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

@@

### do 2-Compartment fit
system.time(
  capture.output(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_2comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""), row.names = FALSE)
